---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw_messy <- read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
  janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}

dat_age_gender <- data_demographics_raw %>% 
rename(date_time= date) %>% 
mutate(group = group + 1)

colnames(dat_age_gender)

#wrangle the demographics data out of the raw
dat_age_gender <- data_demographics_raw |>
#rename for clairty
  rename(unique_id = subject, item = trialcode)|>
  #select useful columns
  select(unique_id, item, response)
#retain rows that we need
temp  <- dat_age_gender |>
  filter(item == "age")

temp <- dat_age_gender|>
  distinct(response)

#check  data type for each column
sapply(dat_age_gender, class)

temp2 <- dat_age_gender|>
  mutate(unique_id_2 = unique_id * 2)|>
  #to replace the original values with the new values and keep the name
  mutate(unique_id = unique_id_2)
  
library(stringr)

temp2 <- dat_age_gender |>
  mutate(response = str_replace_all(response, "\\D"),
response = na_if(response, ""))

#str_remove_all("twenty", "\\D")

  #mutate(response = str_remove_all(response, "[^[:alnum:]]", ""))

  
  
# "age" damit geschriebenes gefunden wird (string matching), ohne "" wird eine Funktion oder ähnliches gesucht
# es kann str_detect (item, "age") verwendet werden um ein string zu finden

# | or operator, & operator

# == qual to

#filter für rows/Zeile

#zwei Formen von Piplines, es können beide verwendet werden

 %>% # tidyverse


|> # base R version

  
  #alle Schritte können verkürzt aufgeschrieben werden. Siehe im Paper von Ian
```

# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 

```

# Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

# Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evalauted as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


